---
title: "Code change"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Code change}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


# Track code changes

You have to download the files from SSB and save it as a `csv` file. For the code changes, they have to be copied and pasted into an Excel file. These code changes can be found under *Endringer* tab in the website. It's advisable to name the file with a specific word to differentiate the file from the `csv` files. I would recommed to add the word `change`. For example `fylke_change_jan2018.xlsx` and the downloaded `csv` file will be `fylke_jan2018.csv`. It's also advisable to add the year to all files to easily differentiate them when running the code. Check the suggested structure [here](https://folkehelseprofil.github.io/norgeo/#file-structure) for naming files.

# Add changes

The `geo_set()` function is the most important function to start with. This function will create an object that is easily used by other available functions in `norgeo`. This is where raw data in `csv` and `xlsx` formats will be merged. Additional information will also be added. The codes below show how the function is used:

```{r add-change, eval=FALSE}
## specify the folder where kommune files are
folder <- "F:/org/kommune"

kom2018 <- geo_set(grep.file = "jan2018",
                   grep.change = "change",
                   year = 2018,
                   type = "kommune",
                   folder.path = folder)

kom2019 <- geo_set(grep.file = "jan2019",
                   grep.change = "change",
                   year = 2019,
                   type = "kommune",
                   folder.path = folder)

kom2020 <- geo_set(grep.file = "jan2020",
                   grep.change = "change",
                   year = 2020,
                   type = "kommune",
                   folder.path = folder)

```

# Merge changes

To merge all these files into a big dataset, use `geo_merge()` function. Important to note that input for `geo_merge()` must be a **list** and they are arranged from oldest to most recent codes. Available output includes:

  - `all`    : All merged codes. This is the default
  - `change` : Only codes that have changed
  - `split`  : Codes that have been divided to at least two codes in the current list
  - `merge`  : At least two codes are merged into one in the current list

```{r merge-geo, eval=FALSE}

komfiles <- list(kom2018, kom2019, kom2020)
DF <- geo_merge(files = komfiles)

# show only codes that have changed
DFS <- geo_merge(files = komfiles, output = "split")

```


# Save codes

The output created from `geo_merge()` i.e `DF`, can be saved in a database management system (DBMS) which include Access and SQLite, or as ordinary files such as Excel or text file.

```{r db, eval=FALSE}
fpath = "C:/Users/ybka/dbms"

geo_save(tblname = "tblTest",
         obj = DF,
         des.path = fpath,
         file.type = "Excel")
```

When saving as a table in a DBMS, a database file must be available prior to saving it. In the example below the object is saved as a table to an Access database `geo_ssb.accdb`.

```{r DBMS, eval=FALSE}
dbpath = "C:/Users/ybka/dbms"
dbname = "geo_ssb.accdb"

geo_save(tblname = "tblGeo",
         obj = bigDF,
         des.path = dbpath,
         file.type = "Access",
         db.name = dbname)
```
