---
title: "Granularity"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Granularity}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


The function `geo_cast()` will add lower granularity to all files when applicable. It means for *kommune* files, a new `fylke` column will be added, while column `fylke` and `kommune` will be added to a *bydel* and *grunnkrets* files.

```{r granularity, eval=FALSE}

## Geo 2019
file2019 <- c("F:/Geo/fylke/fylke_jan2019.csv",
              "F:/Geo/kommune/kommune_jan2019.csv",
              "F:/Geo/bydel/bydel_jan2019.csv",
              "F:/Geo/grunnkrets/grunnkrets_jan2019.csv")

fileTyp2019 <- c("fylke", "kommune", "bydel", "grunnkrets")


DF2019 <- geo_cast(file = file2019,
                   type = fileTyp2019,
                   year = 2019)

## Geo 2020
file2020 <- c("F:/Geo/fylke/fylke_jan2020.csv",
              "F:/Geo/kommune/kommune_jan2020.csv",
              "F:/Geo/bydel/bydel_jan2020.csv",
              "F:/Geo/grunnkrets/grunnkrets_jan2020.csv")

fileTyp2020 <- c("fylke", "kommune", "bydel", "grunnkrets")


DF2020 <- geo_cast(file = file2020,
                   type = fileTyp2020,
                   year = 2020)
```

Running `geo_cast()` will also add a new row for granularity `land` which has code `0`. The output from the above example can then be merged to a file and saved to the file type one wishes. To bind all the output, you can use the base R `rbind()` function or `rbindlist()` function from `data.table` package.

```{r cast, eval=FALSE}
## merge alle dataene
files <- list(DF2019, DF2020)
allCast <- do.call("rbind", files)
```
