---
title: "Use API data"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Use API}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This is a simple guide to access data data via API.

# Download data with API

All functions that has `get_` prefix access data directly via [SSB API](https://data.ssb.no/api/klass/v1/api-guide.html). This is the simple guide to use *norgeo* API functions:

```{r api1, eval=FALSE}
library(norgeo)
dt <- get_code("kommune", from = 2015, to = 2021)
# only current geo code
dt <- get_code("kommune", from = 2021)
```

You could also find geo code changes via `get_change()` function. 

```{r api2, eval=FALSE}
dtc <- get_change("kommune", from = 2015, to = 2021)
```

# Track geo changes

To track all geo changes to the current date specified in the argument `to` can be done as follows:

```{r api3, eval=FALSE}
dtt <- track_change("kommune", from = 2015, to = 2021)
```

You can also track the geo codes that are *split* or *merged* to a new geo with function `track_split()` or `track_merge()`.
